# Welcome to this Sample Document

### Solving quadratic equations

Consider equations of the form $ax^2 + bx + c = 0$. This is a quadratic equation; changing the values of $a$, $b$, and $c$, changes the shape of the quadratic. There are two solutions to a quadratic equation:

$$
x = \dfrac{-b \pm \sqrt{b^2 - 4ac}}{2a}.
$$

Let's draw a quadratic curve for different values of $a, b$, and $c$.

```{r}
a <- 10
b <- 3
c <- -5
x <- seq(-2, 2, length = 1e3)
fx <- a*x^2 + b*x + c
plot(x, fx, type = 'l', xlab = "x", ylab = "Quadratic function")
# adding line for solution
abline(h = 0, lty = 2, col = "red")
```

In the above, we can also change the way the plot appears. I will rerun the above code, without displaying the code, and only producing the plot of figure height "4" units and figure width "4" units

```{r}
#| echo: false
#| fig-cap: "A quadratic function"
#| fig-width: 4
#| fig-height: 4
a <- 10
b <- 3
c <- -5
x <- seq(-2, 2, length = 1e3)
fx <- a*x^2 + b*x + c
plot(x, fx, type = 'l', xlab = "x", ylab = "Quadratic function")
# adding line for solution
abline(h = 0, lty = 2, col = "red")
```

### Studying the Cricket dataset

We will study the cricket dataset more closely now. The `battingbowling.csv` file in your repository contains information regarding various potential all-rounders in men's ODI cricket. The players' batting average, bowling average, and team is present in the dataset.

We will make a few visualizations. But first, we will need a few libraries.

```{r}
library(ggplot2)
library(tibble)
```

Let's load the data the data and convert it to a tibble.

```{r}
cric <- read.csv("battingbowling.csv")
cric <- as_tibble(cric)
cric
```

Let's create a side-by-side boxplot of the Batting averages:

```{r}
#| fig-width: 5
#| fig-height: 3
p <- ggplot(cric, aes(x = Team,y = Batting))
p + geom_boxplot(fill = "tomato")+
  labs(title = "Batting Average", 
       subtitle = "Side-by-side boxplot for Teams", 
       y = "Batting Average")
```

We can do the same thing for the Bowling average as well (notice that I am not showing the code for this)

```{r}
#| echo: false
#| fig-width: 5
#| fig-height: 3
#| fig-align: "center"
p <- ggplot(cric, aes(x = Team,y = Bowling))
p + geom_boxplot(fill = "lightblue")+
  labs(title = "Bowling Average", 
       subtitle = "Side-by-side boxplot for Teams", 
       y = "Bowling Average")
```

Next, we make a scatterplot of the Batting and Bowling average, colored by the Team the player is associated with:

```{r}
#| fig-width: 7
#| fig-height: 4
#| fig-align: "center"
p <- ggplot(cric, aes(x = Batting, y = Bowling))
p + geom_point(aes(color = Team, shape = Team))
```

Additionally, we want to write down, in text, the names of the players with batting average more than 35 and bowling average less than 40. Below is a plot for that.

```{r}
#| echo: false
#| fig-width: 7
#| fig-height: 4
#| fig-align: "center"

foo <- subset(cric,  Batting > 35 & Bowling < 40)

p <- ggplot(cric, aes(x = Batting, y = Bowling))
p + geom_point(aes(color = Team, shape = Team)) + 
  geom_hline(yintercept = 40, color = "tomato", linetype = "dashed") + 
  geom_vline(xintercept = 35, color = "tomato", linetype = "dashed") + 
  geom_text(data = foo, hjust = -.3, 
             aes(x = Batting, y = Bowling, label = X), size = 3)
```

### Some more mathematical equations

Let's practice some mathematical typing.

1.  Consider a rotation matrix:

$$
A = \left(\begin{array}{cc} \cos(\theta) & \sin(\theta) \\ -\sin(\theta) & \cos(\theta) \end{array}  \right)
$$

Our goal is to find the determinant of the above

```{=tex}
\begin{align*}
\text{det}(A) & = \cos(\theta) \cos(\theta) - \sin(\theta) (-\sin(\theta)\\
 & =\sin^2(\theta) + \cos^2(\theta) \\ 
 & = 1 .
\end{align*}
```
2.  Consider the series $A = \sum_{i=1}^{n} i$:

    ```{=tex}
    \begin{align*}
    2A & = \sum_{i=1}^{n} i + \sum_{i=1}^{n} i\\
    & = (1 + 2 + \dots + n) +  (1 + 2 + \dots + n)\\
    & = (1 + n) + (2 + n-1) + \dots (n + 1)\\
     & = n \cdot (n+1)\\
    \Rightarrow A & = \frac{n(n+1)}{2}\,.
    \end{align*}
    ```
